Dynamic Load Balancing for\\Heterogeneous Systems

### 2011-11-29 paper/paper.tex
Added temporary introduction

\section{Introduction}
% The very first letter is a 2 line initial drop letter followed
% by the rest of the first word in caps.
% 
% form to use if the first word consists of a single letter:
% \IEEEPARstart{A}{demo} file is ....
% 
% form to use if you need the single drop letter followed by
% normal text (unknown if ever used by IEEE):
% \IEEEPARstart{A}{}demo file is ....
% 
% Some journals put the first two words in caps:
% \IEEEPARstart{T}{his demo} file is ....
\IEEEPARstart{L}{orem} ipsum dolor sit amet, consectetur adipisicing elit, sed do
eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut
enim ad minim veniam, quis nostrud exercitation ullamco laboris
nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor
in reprehenderit in voluptate velit esse cillum dolore eu fugiat
nulla pariatur. Excepteur sint occaecat cupidatat non proident,
sunt in culpa qui officia deserunt mollit anim id est laborum.

@@

\bibitem{label1}
A.~Lincoln and G.~Washington, \emph{Some Sweet Paper Title}, 3rd~ed. Harlow, England: Addison-Wesley, 1999.

\bibitem{label2}
J.~Smith, \emph{On Having the Most Common Name}, blah blah blah derp derp derp, 2012.

>>>>

\section{Introduction}
% The very first letter is a 2 line initial drop letter followed
% by the rest of the first word in caps.
% 
% form to use if the first word consists of a single letter:
% \IEEEPARstart{A}{demo} file is ....
% 
% form to use if you need the single drop letter followed by
% normal text (unknown if ever used by IEEE):
% \IEEEPARstart{A}{}demo file is ....
% 
% Some journals put the first two words in caps:
% \IEEEPARstart{T}{his demo} file is ....
\IEEEPARstart{L}{everaging} the maximum performance from specialized hardware is one
of the major challenges computer scientists face today.  The unique hardware architecture
of the Graphics Processing Unit (GPU) gives it a place as a massively parallel hardware
accelerator.  However, because of the difficulty in programming for this hardware,
most of the effort is spent on trying to achieve performance from the GPU, while
leaving the CPU unused.  By also using the CPU to process a smaller part of the
data we can achieve higher utilization of resources and therefore increase program
performance.

GPU+CPU co-processing hardly a new idea.  Jimenez et al. \cite{jimenez} present a
dynamic library which can be used in a system to dynamically schedule tasks for GPU
computation across various processes. The method describes only looks at optimizing
usage of the GPU across the whole system, instead of optimizing a single application’s
performance. The StarPU system, on the other hand, presents a method of co-processing
and load balancing on a per application basis \cite{augonnet}. They show that by using an
appropriate model for the load balancing, they are able to achieve improvements in
speed for applications which call for code acceleration multiple times.  We intend
to extend this work to improve the speed of each kernel execution by splitting the
work of that kernel over the capable resources, similar to the schemes used by OpenMP.
Both of these papers address data transfer times as a major cost of GPU computing.
Using the new AMD Fusion architecture, which fuses the CPU and GPU onto a single die,
we may be able to eliminate or greatly reduce this cost, which will impact the overhead
of GPU+CPU co-processing.

We expect that by using GPU+CPU processing we will improve the performance of the
application, when compared to CPU-only or GPU-only.  We will measure performance of the
application using a wall time clock.  We also hypothesize that the fused GPU+CPU
architecture will allow for lower overhead for load balancing.

@@

\bibitem{augonnet}
C.~Augonnet, S.~Thibault, R.~Namyst, and P.A.~Wacrenier,
``StarPU: A Unified Platform for Task Scheduling on Heterogeneous Multicore Architectures'' in
\emph{Proceedings of the 15th International Euro-Par Conference on Parallel Processing}, 2009, pp. 863-874.

\bibitem{che}
S.~Che, M.~Boyer, J.~Meng, D.~Tarjan, J.W.~Sheaffer, S.H.~Lee, and K.~Skadron,
``Rodinia: A benchmark suite for heterogeneous computing'' in
\emph{Proceedings of the 2009 IEEE International Symposium on Workload Characterization (IISWC)}, 2009, pp. 44-54.

\bibitem{danalis}
A.~Danalis, G.~Marin, C.~McCurdy, J.S.~Meredith, P.C.~Roth, K.~Spafford, V.~Tipparaju, and J.S.~Vetter,
``The Scalable Heterogeneous Computing (SHOC) benchmark suite'' in
\emph{Proceedings of the 3rd Workshop on General-Purpose Computation on Graphics Processing Units}, 2010, pp. 63-74.

\bibitem{jimenez}
V.J.~Jiménez, L.~Villanova, I.~Gelado, M.~Gil, G.~Fursin, and N.~Navarro,
``Predictive Runtime Code Scheduling for Heterogeneous Architectures,'' in
\emph{Proceedings of the 4th International Conference on High Performance Embedded
Architectures and Compilers}, 2009, pp. 19-33.
